We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2017-11-10 paper/paper.tex
transition
+2 paragraphs

@@

We then build a multivariate normal distribution for the two halos and
the three variables consistent with a unidimensional normal
distribution using the vector of mean values and covariance matrix.
This means that our final covariance matrix is $6\times 6$ and takes
into account the correlations internal to a single galaxy and with its
partner.

This compact description allows us to generate samples consistent with
the simulations used in their construction.
Finally, we use those generated samples to estimate how commoon are
the deviations from sphericity that we measure in the observational
data.

@@

@@

\subsection{Outlier characterization with a Multivariate Gaussian Model}

Prospects for observational measurement: DESI.

>>>>

We use three dimentional positions as reported by. 
The appendix includes the tables with the values we use in our
computations.
For each central galaxy we use the 15 brightest satellites within a
distance of $300$kpc to the central galaxy.
The satellites for the MW are: 
THe satellites for M31 are:

@@

We then build a multivariate normal distribution for the two halos and
the three variables consistent with a unidimensional normal
distribution using the vector of mean values and covariance matrix.
This means that our final covariance matrix is $6\times 6$ and takes
into account the correlations internal to a single galaxy and with its
partner. 
We compute the preferred covariance matrix and the mean distribution values
with a jackknife technique. 
That is, out of the the $n$ pairs we have, we perfom $n$ different
covariance and mean value measurement using only $n-1$ pairs. 
The reported covariance and mean values correspond to the average of
all measurements, the corresponding standard deviation also help us to
estimate the uncertainty on every reported coefficient.

This compact description allows us to generate samples of size $N$
that are consistent by construction with their parent
simulation. Finally, we use the generated samples to estimate how
commoon are the deviations from sphericity that we measure in the observational
data.  We use a single-tail test in this comparison, meaning that we
always measure the fraction of points with values smaller than the
treshold value.

@@

This is all the information that is needed to compute the fraction of
pairs that are expected to share the same asphericity as the LG.
We start the Discussion section by describing the results of
performing such a computation.

@@
